# Exploratory Data Analysis
This exploratory data analysis (EDA) will be conducted on a training set containing listings data from the San Francisco market for the 48 months between December 2, 2015 and December 4th, 2019. We'll begin by summarizing the datasets that will be used in the study and reviewing the codebook to determine variables to include or exclude.  The core elements of the EDA will then include:

* Univariate analysis including descriptive statistics of the study variables     
* Bivariate analysis using tabular and graphical techniques    
* Multivariate analysis illuminating the relationship among three or more variables.

## Summary of Listings Data
The following summarizes the 48 listings datasets from the San Francisco market from December 2015 through December 2019.
```{python summary, eval=T, echo=F, code=readLines('../notebooks/1.0_data_summary.py')}
```


`r kfigr::figr(label = "eda_summary", prefix = TRUE, link = TRUE, type="Table")`: San Francisco Listings Summary
```{r eda_summary, eval=T, echo=F, results='asis'}
kable(py$summary) %>%
  kable_styling(bootstrap_options=c("striped", "hover", "condensed"), full_width=T)
```
## Columns by Dataset
`r kfigr::figr(label = "eda_columns", prefix = TRUE, link = TRUE, type="Table")`: Columns by Dataset
```{r eda_columns, eval=T, echo=F, results='asis'}
kable(py$columns) %>%
  kable_styling(bootstrap_options=c("striped", "hover", "condensed"), full_width=T)
```

## Codebook

